Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-07 ms.tex
starting optical extinction/reddening discussion

%FILL THIS SECTION IN !!!!!

>>>>

While the dust temperature and optical depth maps thus far derived are
useful for making predictions of thermal dust foreground emission, 
estimating optical reddening/extinction is another important application of the
optical depth map. We choose to calibrate to empirically to reddening,
rather than make additional assumptions about the dust grain size distribution
and physics that would be necessary to perform an analytic calculation.

To achieve this empirical calibration, we must adopt a set of ``calibrators''
for which true reddening is known. There are various possibilities
at our disposal. SFD used XX. \cite{planckdust} used quasars. Here we use
the SSPP stars with SDSS spectra and photometry studied by \cite{schlafly10}.

Information from the spectral lines of these SSPP stars can be used, along with
 a library of synthetic stellar spectra, to predict the true optical broadband 
colors. The `true' reddening then is simply the difference in the observed
$g-r$ color and the $g-r$ color predicted from the spectral lines. This
gives us $E(B-V)$ estimates for $\sim$250,000 lines of sight, mostly at
high Galactic latitude. The calibration of two-component optical depth
to $E(B-V)$ is then performed as a linear regression of $E(B-V)_{SSPP}$ versus
$\tau_{545}$. The results of this regression are shown in Figure 
\ref{fig:calib}. Indeed there appears to be a strong linear relation
between $E(B-V)_{SSPP}$ and $\tau_{545}$ The conversion factor from 
$\tau_{545}$ to $E(B-V)$ is $\sim$2400.
